Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-05 Paper.tex
e was with a tilde not an umlaut. Updated hypertarget for T w.

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
\usepackage[utf8]{inputenc}
%This character renders, so this shouldn't be needed: \DeclareUnicodeCharacter{C3}{\"{e}}
%For testing: \DeclareUnicodeCharacter{AD}{\Huge [ICI]}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

\begin{description}
\hypertarget{T n}{
\item[nonce] \label{itm:nonce} A scalar value equal to the number of transactions sent by the sender; formally $T_\mathbf{n}$.}\hypertarget{T p}{
\item[gasPrice] A scalar value equal to the number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_\mathbf{p}$.}\hypertarget{T g}{
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be increased later; formally $T_\mathbf{g}$.}\hypertarget{T t}{
\item[to] The 160-bit address of the message call's recipient or, for a contract creation transaction, $\varnothing$, used here to denote the only member of $\mathbb{B}_0$ ; formally $T_\mathbf{t}$.}\hypertarget{T v}{
\item[value] A scalar value equal to the number of Wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created account; formally $T_\mathbf{v}$.}
\item[v, r, s] Values corresponding to the signature of the transaction and used to determine the sender of the transaction; formally \hyperlink{T w}{$T_\mathbf{w}$}, \hyperlink{T r}{$T_\mathbf{r}$} and \hyperlink{T s}{$T_\mathbf{s}$}. This is expanded in Appendix \ref{app:signing}.
\end{description}

@@

We assert the functions $\mathtt{\small ECDSAPUBKEY}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSASIGN}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom} and \cite{ECDSAWikipedia}. \footnote{For the former citation, refer to section 6.2 for ECDSAPUBKEY, and section 7 for ECDSASIGN and ECDSARECOVER.} %(assuming that the former is for signature generation and the latter is for signature verification)
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\ e = \mathtt{\small HASH}(m) \\
\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

@@

\hypertarget{T w}{}\hypertarget{T r}{}\hypertarget{T s}{The signed transaction $G(T, p_r)$ is defined as:
\begin{eqnarray}
G(T, p_r) \equiv T \quad \text{except:} \\
(\hyperlink{T w}{T_\mathbf{w}}, T_r, T_s) = \mathtt{\small ECDSASIGN}(h(T), p_r)
\end{eqnarray}}

>>>>

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
%\usepackage[utf8]{inputenc}
%This character renders, so this shouldn't be needed: \DeclareUnicodeCharacter{C3}{\"{e}}
%For testing: \DeclareUnicodeCharacter{AD}{\Huge [ICI]}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

\begin{description}
\hypertarget{T n}{
\item[nonce] \label{itm:nonce} A scalar value equal to the number of transactions sent by the sender; formally $T_\mathbf{n}$.}\hypertarget{T p}{
\item[gasPrice] A scalar value equal to the number of Wei to be paid per unit of \textit{gas} for all computation costs incurred as a result of the execution of this transaction; formally $T_\mathbf{p}$.}\hypertarget{T g}{
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be increased later; formally $T_\mathbf{g}$.}\hypertarget{T t}{
\item[to] The 160-bit address of the message call's recipient or, for a contract creation transaction, $\varnothing$, used here to denote the only member of $\mathbb{B}_0$ ; formally $T_\mathbf{t}$.}\hypertarget{T v}{
\item[value] A scalar value equal to the number of Wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created account; formally $T_\mathbf{v}$.}\hypertarget{T w}{
\item[v, r, s] Values corresponding to the signature of the transaction and used to determine the sender of the transaction; formally {$T_\mathbf{w}$}}, \hyperlink{T r}{$T_\mathbf{r}$} and \hyperlink{T s}{$T_\mathbf{s}$}. This is expanded in Appendix \ref{app:signing}.
\end{description}

@@

We assert the functions $\mathtt{\small ECDSAPUBKEY}$, $\mathtt{\small ECDSARECOVER}$ and $\mathtt{\small ECDSASIGN}$. These are formally defined in the literature, \eg by \cite{ECDSAcerticom} and \cite{ECDSAWikipedia}.
\begin{eqnarray}
\mathtt{\small ECDSAPUBKEY}(p_r \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64} \\
\ e & \equiv & \mathtt{\small HASH}(m) \\
\mathtt{\small ECDSASIGN}(e \in \mathbb{B}_{32}, p_r \in \mathbb{B}_{32}) & \equiv & (v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) \\
\mathtt{\small ECDSARECOVER}(e \in \mathbb{B}_{32}, v \in \mathbb{B}_{1}, r \in \mathbb{B}_{32}, s \in \mathbb{B}_{32}) & \equiv & p_u \in \mathbb{B}_{64}
\end{eqnarray}

@@

\hyperlink{T w}{}\hypertarget{T r}{}\hypertarget{T s}{The signed transaction $G(T, p_r)$ is defined as:
\begin{eqnarray}
G(T, p_r) \equiv T \quad \text{except:} \\
(\hyperlink{T w}{T_\mathbf{w}}, T_r, T_s) = \mathtt{\small ECDSASIGN}(h(T), p_r)
\end{eqnarray}}
